Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
1 sentence per line
criteria -> criterion

Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by equation (\ref{eq:fplasmalos_scaled}). 
The doubly hatched regions in Figure \ref{fig:radio} indicate the parameter spaces where the criteria $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ is not satisfied and thus the radio emission from the planet cannot be observed from the Earth. 
In reality, the peak of the auroral radio emission does not always occur at the maximum frequency. Instead, it usually exits at lower frequencies. Here, we also consider one more criteria, $0.1 \nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ as a conservative measure for the observability of the bulk of radio emission. In Figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines. 
It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars. 
For a red-giant system, the most promising targets are massive companions with $M_p \gtrsim 4M_{\rm J}$, while the smaller ones at distant orbits are also accessible.  
On the other hand, for a AGB-star system, only very massive planets at distant orbits are marginally detectable.

>>>>

Observable energy flux is, however, limited by the plasma cut-off frequency in the vicinity of the planets, given by equation (\ref{eq:fplasmalos_scaled}). 
The doubly hatched regions in Figure \ref{fig:radio} indicate the parameter spaces where the criteria $\nu_{\rm cyc,\,max} > \nu_{\rm plasma}^{\rm los}$ is not satisfied and thus the radio emission from the planet cannot be observed from the Earth. 
In reality, the peak of the auroral radio emission does not always occur at the maximum frequency.
Instead, it usually exits at lower frequencies.
Here, we also consider one more criterion, $\nu_{\rm cyc,\,max} > 10 \nu_{\rm plasma}^{\rm los}$ as a conservative measure for the observability of the bulk of radio emission.
In Figure \ref{fig:radio}, this conservative region is shown as hatched regions with vertical lines. 
It is now shown that the plasma cut-off due to massive stellar wind is a major obstacle in detecting planetary companions around evolved stars. 
For a red-giant system, the most promising targets are massive companions with $M_p \gtrsim 4M_{\rm J}$, while the smaller ones at distant orbits are also accessible.  
On the other hand, for a AGB-star system, only very massive planets at distant orbits are marginally detectable.
